Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
corrigindo largura das figuras

\begin{figure}[t]
  \centering
  \includegraphics[trim=0 0 0 0,clip,width=0.85\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure
    overview.\Fix{tem certeza que Hermes estah usando mesma fonte/tamanho?}}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[trim=0 330 170 0,clip,width=0.85\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure
    overview.}
\end{figure}
